\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-07-28 syntax.tex
Reply the comments
reply to comment

Now, together with sealing, we can read \ruleref{Sig Add} and
\ruleref{Lnkg Add} out clearly: given a constructed linkage $o : \cL\sigma$
of signature $\sigma$, the next added field $t : T$ will have
to be in the context of the abstraction $A$\YZ{Why do Lnkg Add and Sig Add leave A unspecified? I thought this A corresponds to 'self'.}\EDJreply{It is not unspecified. I now change it so that it is more clear. It is parametric as well. Just note that when specifying the abstraction `A', the seal `f' has to be specified at the sametime. (Thus I omitted it initially because it is implicitly specified w.r.t. the speicifcation of `f') }\YZreply{
  Changed what? I think Lnkg Add and Sig Add were not changed.
  I still don't see how sealing converts \cC \{a : \bW sigma ; ..\} to \cC\{a : \cU ; ..\}
  and how the latter is now used as the abstracted A.
}\EDJreply{I added the $\goodType{\Gamma}{A}{}$  as you suggested. \\
\cC \{a : \bW sigma ; ..\} is definitionally equal to a sigma type as Compile rule suggested. \\
If you expand the definition, you will see two sigma type. 
You are asking where is the function \cC \{a : \bW sigma ; ..\} to \cC\{a : \cU ; ..\}, which by definition is requesting (Sigma (a : \bW sigma ; ..)) to (Sigma (a : \cU ; ..)). \\
This is something doable in vanilla MLTT, with the help of transforming \bW sigma to \cU, by rule `Ind-Type'. }
of the compilation $\cC\sigma$ (witnessed by the seal $f$).
The ``concatenation'' of the
$o$ and $t$ leads to a new linkage, of which the signature is the
``concatenation'' of the $\sigma$ and $T$ (we also record the sealing
$f$ for simplicity). The key here is our signature, will \textit{record}
this abstraction witness $f$,\YZ{Why is it necessary to record the witness f? I don't see how p_f nu is needed anywhere.}\EDJreply{1. this is for the sake of eta/beta rule (local soundness + local completeness); 2.It is actually used in the rule Compile (the last one), if Ct is compile a variable, say ``Ct v'', then this ``Ct v = (Ct p_1 v), (t[sf p_f v][...])'', the f will actually be replaced by p_f; 3. p_f can be used by the user. It doesn't have to interact with other typing rules. }
thus any projected member will still be in
the abstracted context and thus possibly \textit{inheritable}.  The
construction of linkage in \ruleref{Lnkg Add} requires $t$ to
\textbf{only} refer to the (abstraction $A$ of) former part of the
defining family $o : \cL\sigma$, this is to avoid inconsistency
mentioned in \ref{chg:consistency} in metatheory.

>>>>

Now, together with sealing, we can read \ruleref{Sig Add} and
\ruleref{Lnkg Add} out clearly: given a constructed linkage $o : \cL\sigma$
of signature $\sigma$, the next added field $t : T$ will have
to be in the context of the abstraction $A$\YZ{Why do Lnkg Add and Sig Add leave A unspecified? I thought this A corresponds to 'self'.}\EDJreply{It is not unspecified. I now change it so that it is more clear. It is parametric as well. Just note that when specifying the abstraction `A', the seal `f' has to be specified at the sametime. (Thus I omitted it initially because it is implicitly specified w.r.t. the speicifcation of `f') }\YZreply{
  Changed what? I think Lnkg Add and Sig Add were not changed.
  I still don't see how sealing converts \cC \{a : \bW sigma ; ..\} to \cC\{a : \cU ; ..\}
  and how the latter is now used as the abstracted A.
}\EDJreply{I added the $\goodType{\Gamma}{A}{}$  as you suggested. \\
\cC \{a : \bW sigma ; ..\} is definitionally equal to a sigma type as Compile rule suggested. \\
If you expand the definition, you will see two sigma type. 
You are asking where is the function \cC \{a : \bW sigma ; ..\} to \cC\{a : \cU ; ..\}, which by definition is requesting (Sigma (a : \bW sigma ; ..)) to (Sigma (a : \cU ; ..)). \\
This is something doable in vanilla MLTT, with the help of transforming \bW sigma to \cU, by rule `Ind-Type'. And this function's type should be directly the sealing type.}\YZreply{
  My confusion is this: it seems that in Lnkg Add and Sig Add, A could well be the top type and f a value of the top type. In this sense, A seems unspecified.
}
of the compilation $\cC\sigma$ (witnessed by the seal $f$).
The ``concatenation'' of the
$o$ and $t$ leads to a new linkage, of which the signature is the
``concatenation'' of the $\sigma$ and $T$ (we also record the sealing
$f$ for simplicity). The key here is our signature, will \textit{record}
this abstraction witness $f$,
%\YZ{Why is it necessary to record the witness f? I don't see how p_f nu is needed anywhere.}\EDJreply{1. this is for the sake of eta/beta rule (local soundness + local completeness); 2.It is actually used in the rule Compile (the last one), if Ct is compile a variable, say ``Ct v'', then this ``Ct v = (Ct p_1 v), (t[sf p_f v][...])'', the f will actually be replaced by p_f; 3. p_f can be used by the user. It doesn't have to interact with other typing rules. }
thus any projected member will still be in
the abstracted context and thus possibly \textit{inheritable}.  The
construction of linkage in \ruleref{Lnkg Add} requires $t$ to
\textbf{only} refer to the (abstraction $A$ of) former part of the
defining family $o : \cL\sigma$, this is to avoid inconsistency
mentioned in \ref{chg:consistency} in metatheory.
